Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-15 DGMM2025/paper.tex
added gridstep vs mean visibility distance plot

\usepackage{changes}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{varwidth}
\usepackage{mathtools}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices}

@@

@@

>>>>

\usepackage{changes}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{varwidth}
\usepackage{mathtools}
\usepackage{pgfplots}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

@@

        \caption{Representation of a 2d cell complex (here the star of a given curve) as lattices. From X cells from the star on the left, we get Y intervals on the right}

@@

    \pgfplotsset{width=13cm}
    \begin{tikzpicture}
        \centering
        \begin{axis}[
            xlabel={Gridstep},
            x dir=reverse,
            ylabel={Mean distance},
            legend pos=north west,
            ymajorgrids=true,
            grid style=dashed,
            ymode=log,
            log ticks with fixed point,
        ]

            \addplot[
                color=cyan,
                mark=square,
            ]
            coordinates {
                (1,5.76973)(0.875,6.03836)(0.75,6.22426)(0.625,6.39012)(0.5,6.51014)(0.375,6.63571)(0.25, 6.68132)
            };
            \addlegendentry{sphere9 radius 10}
            \addplot[
                color=red,
                mark=square,
            ]
            coordinates {
                (1,5.91022)(0.875,6.10641)(0.75,6.14175)(0.625,6.20202)(0.5,6.28637)(0.375,6.44418)(0.25, 6.56938)
            };
            \addlegendentry{goursat radius 10}
            \addplot[
                color=red,
                mark=triangle,
            ]
            coordinates {
                (1,9.04228)(0.875,10.1319)(0.75,10.2837)(0.625,10.6125)(0.5,10.8969)(0.375,11.3186)(0.25, 11.8382)
            };
            \addlegendentry{radius 20}
            \addplot[
                color=red,
                mark=halfcircle,
            ]
            coordinates {
                (1,9.22083)(0.875,10.6476)(0.75,11.5976)(0.625,12.7428)(0.5,13.9534)(0.375,14.73)(0.25,15.8425)
            };
            \addlegendentry{radius 30}
            \addplot[
                color=violet,
                mark=square,
            ]
            coordinates {
                (1,5.36873)(0.875,5.43148)(0.75,5.47206)(0.625,5.67227)(0.5,5.81554)(0.375,6.03961)(0.25,6.31671)
            };
            \addlegendentry{torus}
            \addplot[
                color=violet,
                mark=triangle,
            ]
            coordinates {
                (1,6.42158)(0.875,6.36929)(0.75,6.94675)(0.625,7.65529)(0.5,8.65652)(0.375,9.05402)(0.25,10.0784)
            };
            \addplot[
                color=violet,
                mark=halfcircle,
            ]
            coordinates {
                (1,6.44119)(0.875,6.43563)(0.75,7.00852)(0.625,7.71613)(0.5,9.1544)(0.375,9.84299)(0.25,12.241)
            };
        \end{axis}
    \end{tikzpicture}
